master thesis

### 2018-03-30 Paper - Latex/Paper - Skizze - v4.tex
Thesis - describe table ...

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Real data analysis} \label{sec:methods - real data analysis}
    For the evaluation of real data results, a leave-100-out cross-validation is performed. For this 
      purpose 100 randomly distributed 100 states are left out.

    Analogous to the missing leaf node states, generalized linear models with binomial regression are 
      compared according to their residuals, based on the "true" / "false" prediction. \\
    Again, in order to compare models of different complexity, the BIC (Bayesian Information Criterion) 
      values are calculated in addition to the residuals. \\
    For all these calculations, the following R functions are used: \textit{glm()}, \textit{anova()} 
      and \textit{BIC()}. \\

@@

  As a result, we used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. 
    \cite{Louca2017}, which performed best, for the actual reconstruction on the real data. \\
    \todo{... biological view}
  %  On the one hand, we have examined the results of some 
    % subtrees for their credibility with the help of biological background knowledge (subsection 
    % \ref{sec:results - biological view}). On the other hand, we
  We evaluated these by performing a leave-100-out cross-validation and predicted approximately 
    98.17\% of the omitted states correct (subsection \ref{sec:results - cross-validation}). \\

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of the real data analysis created with Sankoff}
    This section is about evaluating the prediction of real data using the Sankoff method. \\
    It is divided into two subsections. \ref{sec:results - biological view}: The analysis of some subtrees using 
      biological background knowledge. \ref{sec:results - cross-validation}: Presentation of the results 
      of the leave-100-out cross-validation.

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Biological view} \label{sec:results - biological view}
      To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
        Apicomplexa. \\
      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
      Several factors such as the distribution of existing input data via parasitics and free-livings, 
        faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
        role, which crystallize out in these examples. \\
      An important factor here is the credibility of the results. The accuracy of the input data 
        stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
        input data can be amplified by incorrect prediction of unknown species and can be reversed in 
        order to improve the data situation of GloBI. \\
      Since we look at such large trees we can not expect to know all the parasites, so we look at 
        individual positives. This is positive in the sense that the majority have the opposite state.

      \newcommand*\rot{\rotatebox{90}}

@@

            & \bfseries Taxa & \bfseries \#internal & \bfseries \#leaf 
                & \multicolumn{2}{>{\scriptsize}c||}{\bfseries known states} & \multicolumn{3}{>{\scriptsize}c|}{\bfseries final states}

@@

            & \bfseries subtree & \multicolumn{2}{>{\scriptsize}c||}{\bfseries nodes} & \bfseries FL & \bfseries P

@@

            & \bfseries & & & & 

@@

                & state & \bfseries FL $\rightarrow$ P & \bfseries P $\rightarrow$ FL \\

@@

            & Chloro- & 43486 & 416478          & 3519 & 77         & 410795 & 4182 & 1501        & 0.5 & 97 & 222 \\
            & plastida & &                      & 97.86\% & 2.14\%  & 98.63\% & 1.00\% & 0.36\%   & & & \\ \cline{2-12}

@@

            & & &                               & 0.39\% & 99.61\%  & 0.05\% & 0\% & 99.95\%      & P & & \\ \cline{2-12}

@@

            & & &                               & 62.93\% & 37.07\% & 91.78\% & 1.87\% & 6.34\%   & FL & & \\ \cline{2-12}

@@

            & & &                               & 99.83\% & 0.49\%  & 99.97\% & 0\% & 0.03\%      & FL & & \\ \cline{2-12}

@@

            & & &                               & 0.63\% & 99.37\%  & 5.79\% & 3.97\% & 90.23\%   & P & & \\ \cline{2-12}
            & Platyhel- & 4459 & 22683       & 7 & 7086          & 175 & 0 & 22508             & 0 & 0 & 5 \\
            & minthes & &                          & 0.1\% & 99.9\%    & 0.77\% & 0\% & 99.23\%      & P & & \\

@@

            & & &                               & 62.44\% & 37.56\% & 94.63\% & 0.09\% & 5.28\%   & FL & & \\ 

@@

        \caption{Some selected phyla (subtrees), only leaf nodes, are examined for the evolution 
          of the amount and percentage of given data to predicted data.}
          % \caption{All kingdoms (subtrees), only leaf nodes, are examined for the evolution of the 
          % amount and percentage of given data to predicted data.}
          % \caption{Origins and losses}
        \label{table:phylum leaf nodes states} 

@@

      \begin{table}[H]
        \centering
        \begin{tabular}{|c|l|r|r|r|r|}
        \hline
        & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{Text} & \multicolumn{1}{c|}{text}\\
        \hline
        \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{rota}}} & text &&&&\\
        & text &&&&\\
        & text &&&&\\
        \hline
        \end{tabular}
        \end{table}

      In contrast to the other phyla examined, the phylogeny in the Chordata is more pronounced (less 
        multifurcation) (see Table \ref{table:percentage loss information subtrees}). This results in 
        less variance of errors. What is reflected in the results from the table 
        \ref{table:phylum leaf nodes states}. There are 18 parasites as input data and only 8 more are 
        predicted. The Chordata mostly consist of free-living species, so this seems believable. We 
        started with 99.83\%  species and predict 99.97\% species as free-living (including already 
        known nodes).

      We mapped the few parasitic species in a \colorbox{red}{rough/simple} taxonomy (see Figure \ref{fig:ChordataParasites}): \\
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
        got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
        \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
        known as broodparasite and some others. \\
      An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
        concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
        (\textit{Cyprinus carpio})\footnote{
          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
          {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
        }. Since there is hardly any information about free-living, it follows that all siblings are 
        also predicted to be parasitic. \\
        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
        % Snake: Storeria dekayi (probably caused by wrong input data.)
      % \begin{itemize}
      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
      %     they eat fin or pieces of larger fish.
      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
      %     species in here.
      % \end{itemize}

      Most species of Platyhelminthes (flatworms) are parasites, although there are also free-living, 
        predatory feeding species. These are summarized in the Turbellaria, while the parasites are 
        divided into three other classes \cite{Ax1961}. This also corresponds to our observations. There 
        is one class (Rhabditophora) that contains all but one single exception of free-living species 
        of this phylum, which includes the Turbellaria. \\
      It should be noted, however, that this classification is outdated, as it has been proven that 
        the Turbellaria are not monophyletic. But we will not go into that here. \\
      For the Platyhelminthes we have more state information for the leaf nodes compared to the other 
        considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
        0.1\% free-livings and predicted 0.77\% as free-living species. \\

      With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
        found only 5.32\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosed parasitism 
        \cite{Blaxter1998}. In a recent article Blaxter identifies 18 origins \cite{Blaxter2015} in 
        Nematoda. \\
      The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species 
        are described by the Nematoda but is it assumed that one million or more species are in this 
        phylum.\footnote{J. Hallan, unpublished; 
          \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
          {https://insects.tamu.edu/research/collection/hallan/}
        }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
        with only 0.63\% (table \ref{table:phylum leaf nodes states}) free-living species. Against such 
        a shifted data situation, the algorithm is almost powerless to make correct predictions. And yet 
        the percentage has increased to 5.34\%. \\

      \todotext{Im Folgenden folgen 3 weitere ähnliche tabellen. Einmal eine ähnliche Tabelle inklusive 
        interner Knoten \ref{table:Phylum internal nodes}, zweimal die Übersicht über die Kingdoms 
        Blattknoten \ref{table:Kingdom leaf nodes} bzw interne Knoten \ref{table:Kingdom internal nodes}. Welche 
        nehmen wir? Rest Appendix oder ganz raus?}

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Origins and Losses} \label{sec:results - origins and losses}

        Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
          They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
          in Insecta. \\
        This has led us to count the origins and losses of parasitism in our investigation as well. \\
        We count only one origin / loss in a parent node with different children's nodes. \\
        Here we have encountered a problem: The Castor algorithm gives us probabilities for states. That 
          means there are also nodes with state like 0.3 or 0.5. The question is, how to count these state 
          changes. We decided to round the values.
        % \begin{lstlisting}[gobble=6]
        %   possible states: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
        %   rounded to:    0  0      0    0    1      1     1
        % \end{lstlisting}

        In Table \ref{table:origins and losses} we can see, that we found some more origins than Weinstein 
          and on top of that some losses. \\

        When more closely regarding the same phyla as in the section before: Chordata, Nematoda, 
          Platyhelminthes and Apicomplexa. \\
        Chordata are full of free-living species and so we see only a few origins of parasitism. The root
        and mostly all species are predicted as free-living. \\
        In Apicomplexa and the Platyhelminthes also look credible. Our algorithm gives us only one loss of
          parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over
          mostly all species predicted as parasites. \\
        Nematoda is again full of problems. The root node is predicted as a parasite and so we have more 
          losses of parasitism for the less information of free-living species in this phylum. The rest 
          is parasitic \\
        As we have already mentioned Blaxter et al. found at least seven origins of parasitism 
          \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
          losses would have to turn around and become Origins. So it could be that we end up in a similar 
          size as Blaxter.

@@

@@

    From the simulation, we can conclude that we predict correctly about 60\% of the nodes in the 
      present data situation (see section \ref{sec:results - simulation}).
    The leave-100-out cross-validation even showed that we predict the omitted nodes to be 98.17\%  
      percent correct (see section \ref{sec:results - cross-validation}). \\
    This allows for the assumption that the data is grouped and not uniformly distributed and thus 
      smaller subtrees are present in which data are to be found in the simulation with smaller 
      multifurcation and smaller value for unknown nodes. This is also confirmed by our biological 
      analysis of the Chordata subtree (see subsection \ref{sec:results - biological view}). \\
    However, this means that the ancestral states' data in the direction of root node are probably 
      particularly unbelievable. Which makes the localization of Origins direction root node 
      difficult. The question remains, how much this affects the estimation of the number of origins. 
      Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} (see subsection 
      \ref{sec:results - origins and losses}), however, leaves us with optimism.

@@

  %---------------------------------------------------------------------------------------------------
  \section{Results}

    \begin{table}[h!]
      \begin{center}
        \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
          \hline
          & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{6}{c|}{\bfseries final states} \\
          \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P
            & \bfseries 0 (FL) & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
          \hline \hline
          Chordata & 122546 & 10451 & 18 
            & 122473 & 0 & 0 & 0 & 0 & 73 \\
          Nematoda & 33564 & 21 & 3289 
            & 846 & 0 & 1133 & 0 & 0 & 31585 \\
          Platyhelminthes & 27142 & 7 & 7086 
            & 1010 & 0 & 175 & 0 & 0 & 25957 \\
          Apicomplexa & 2102 & 1 & 255 
            & 1 & 0 & 0 & 0 & 0 & 2101 \\
          % \hline
          % Arthropoda & 1319460 & 18912 & 11141 
          %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
          \hline
        \end{tabular}
      \end{center}
      \caption{Some selected phyla (subtrees), including internal nodes, are examined for the evolution 
      of the amount and percentage of given data to predicted data.}
      \label{table:Phylum internal nodes}
    \end{table}

    \begin{table}[h!]
      \begin{center}
        \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
          \hline
          & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
          \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
            & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
          \hline \hline
          none & 84456 & 45 & 529 
            & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
          Fungi & 324105 & 577 & 2983
            & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
          Chloroplastida & 460457 & 3519 & 77
            & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
          Metazoa & 1670956 & 30758 & 22373
            & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
          \hline  
        \end{tabular}
      \end{center}
      \caption{All kingdoms (subtrees), inkluding internal nodes, are examined for the evolution of the 
      amount and percentage of given data to predicted data.}
      \label{table:Kingdom internal nodes}
    \end{table}

>>>>

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Real data analysis} \label{sec:methods - real data analysis}
    For the evaluation of real data results, some statistics are collected and a leave-100-out 
      cross-validation is performed. For this purpose 100 randomly distributed 100 states are left out.

    The statistics are collected over the entire Eukaryota tree and over some subtrees of different 
      taxa. There are known states besides predicted states, the predicted root node state specified 
      and origins and losses are counted by parasitism. \\
    Since Sankoff predicts probabilities for states, we have rounded them to be able to count 
      transitions from free-living (0) to parasitic (1) and vice versa. \\
    In each case, a maximum of one changing transition from parent node to child node is counted for 
      the origins (FL $\rightarrow$ P) or losses (P $\rightarrow$ FL).

    For the leave-100-out cross-validation, analogous to the missing leaf node states, generalized 
      linear models with binomial regression are compared according to their residuals, based on the 
      "true" / "false" prediction. \\
    Again, in order to compare models of different complexity, the BIC (Bayesian Information Criterion) 
      values are calculated in addition to the residuals. \\
    For all these calculations, the following R functions are used: \textit{glm()}, \textit{anova()} 
      and \textit{BIC()}. \\

@@

  As a result, we used the Sankoff algorithm \cite{Sankoff1975} implemented by Louca et al. 
    \cite{Louca2017}, which performed best, for the actual reconstruction on the real data. \\
    \todo{... biological view}
  %  On the one hand, we have examined the results of some 
    % subtrees for their credibility with the help of biological background knowledge (subsection 
    % \ref{subsec:results - statistics on predicted states}). On the other hand, we
  We evaluated these by performing a leave-100-out cross-validation and predicted approximately 
    98.17\% of the omitted states correct (subsection \ref{sec:results - cross-validation}). \\

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of the real data analysis created with Sankoff}
    This section is about evaluating the prediction of real data using the Sankoff method. It is 
      divided into two subsections. The analysis of some statistics on the predicted states, 
      \todo{with the result...} (subsection \ref{subsec:results - statistics on predicted states}) and the presentation 
      of the leave-100-out cross-validation results (subsection \ref{sec:results - cross-validation}).
      \todo{This has revealed that ...} \\

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Statistics on predicted states} \label{subsec:results - statistics on predicted states}
      In the entire Eukaryota tree we start with 57.31\% free-living species and 42.69\% parasites. The 
        prediction yields 80.98\% free-livings 0.31\% undefinable and 18.71\% parasites. In addition, 
        there are 462 origins of parasitism and 369 losses distributed throughout the tree, with the 
        root node predicted to be parasitic. \\
      We have predicted significantly more free-livings than parasites, but parasitism has prevailed to 
        the root node.

      In table \ref{table:results of some selected taxa} we compare different subtrees of different taxa 
        on these prediction results.

      Similar to the Eukaryota it is with the Metazoa subtree, which accounts for most of the Eukayota 
        (179,944 internal and 1,491,012 leaf nodes). However, here the root node is no longer calculated 
        as parasitic but still as indefinable. \\
      Strongly parasitic subtrees are for example the Apicomplexa, the Nematoda and the Platyhelminthes. 
        For all three, the prediction is at a similar proportion between input values of the states and 
        predicted states, e.g. In the Apicomplexa with 99.61\% known parasitic states, 99.95\% parasites 
        were predicted. The same applies to the chordata, only that these mainly consist of free-living 
        species.

@@

            \multirow{3}{*}{\rot{\bfseries $\leftarrow$ Taxa}}
            & & \multicolumn{2}{>{\scriptsize}c||}{\bfseries number of}
                & \multicolumn{2}{>{\scriptsize}c||}{\bfseries known states} & \multicolumn{3}{>{\scriptsize}c||}{\bfseries final states}

@@

            & \bfseries Subtree & \bfseries internal & \bfseries leaf & \bfseries FL & \bfseries P

@@

            & \bfseries & \multicolumn{2}{>{\scriptsize}c||}{\bfseries nodes} & &

@@

                & \bfseries state & \bfseries FL $\rightarrow$ P & \bfseries P $\rightarrow$ FL \\

@@

            & Chloroplastida & 43486 & 416478   & 3519 & 77         & 410795 & 4182 & 1501        & 0.5 & 97 & 222 \\
            & & &                               & 97.86\% & 2.14\%  & 98.63\% & 1.00\% & 0.36\%   & & & \\ \cline{2-12}

@@

            & {\tiny (Chloroplastida)\par} & &  & 0.39\% & 99.61\%  & 0.05\% & 0\% & 99.95\%      & P & & \\ \cline{2-12}

@@

            & {\tiny (Metazoa)\par} & &         & 62.93\% & 37.07\% & 91.78\% & 1.87\% & 6.34\%   & FL & & \\ \cline{2-12}

@@

            & {\tiny (Metazoa)\par} & &         & 99.83\% & 0.49\%  & 99.97\% & 0\% & 0.03\%      & FL & & \\ \cline{2-12}

@@

            & {\tiny (Metazoa)\par} & &         & 0.63\% & 99.37\%  & 5.79\% & 3.97\% & 90.23\%   & P & & \\ \cline{2-12}
            & Platyhelminthes & 4459 & 22683    & 7 & 7086          & 175 & 0 & 22508             & 0 & 0 & 5 \\
            & {\tiny (Metazoa)\par} & &         & 0.10\% & 99.9\%   & 0.77\% & 0\% & 99.23\%      & P & & \\

@@

            & {\tiny (Arthropoda)\par} & &      & 62.44\% & 37.56\% & 94.63\% & 0.09\% & 5.28\%   & FL & & \\ 

@@

        \caption{Results of some selected taxa (subtrees). \\
          (1 + 2) subtree taxa and name; 
          (3 + 4) number of internal nodes and leaf nodes; 
          (5 + 6) number or percentage of known states; 
          (7 - 9) number or percentage of predicted states; 
          (10) predicted state of the root node of the subtree; 
          (11 + 12) origins and losses with rounded states.}
          \label{table:results of some selected taxa}

@@

      Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
        They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
        in Insecta. \\
      In Table \ref{table:results of some selected taxa} we can see, that we found some more origins than 
        Weinstein: 321 in Metazoa $\supset$ 281 in Arthropoda $\supset$ 245 in Insecta and on top of 
        that some losses: 129 in Metazoa $\supset$ 108 in Arthropoda $\supset$ 77 in Insecta. The 
        origins and losses calculated by Sankoff are thus closer to the leaves in the tree.

@@

To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
Apicomplexa. \\

Several factors such as the distribution of existing input data via parasitics and free-livings, 
faulty input data from GloBI and reinforcement of errors by multifurcation play an important role which becomes evident in these examples. \\

An important factor here is the credibility of the results. The accuracy of the input data 
stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
input data can be amplified by incorrect prediction of unknown species and can be reversed in 
order to improve the data situation of GloBI. \\
Since we look at such large trees we can not expect to know all the parasites, so we look at 
individual positives. They are positive in the sense that the majority have the opposite state.

In contrast to the other phyla examined, the phylogeny in the Chordata is more pronounced (less 
        multifurcation) (see Table \ref{table:percentage loss information subtrees}). This results in 
        less variance of errors. What is reflected in the results shown in table 
        \ref{table:results of some selected taxa}. There are 18 parasites as input data and only 8 more are 
        predicted. The Chordata mostly consist of free-living species, so this seems believable. We 
        started with 99.83\%  species and predict 99.97\% species as free-living (including already 
        known nodes).

      We mapped the few parasitic species in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild here that are 
        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
        got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
        \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
        known as broodparasite and some others. \\
      An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
        concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
        (\textit{Cyprinus carpio})\footnote{
          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
          {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
        }. Since there is hardly any information about free-living, it follows that all siblings are 
        also predicted to be parasitic. \\
        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
        % Snake: Storeria dekayi (probably caused by wrong input data.)
      % \begin{itemize}
      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
      %     they eat fin or pieces of larger fish.
      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
      %     species in here.
      % \end{itemize}

      Most species of Platyhelminthes (flatworms) are parasites, although there are also free-living, 
        predatory feeding species. These are summarized in the Turbellaria, while the parasites are 
        divided into three other classes \cite{Ax1961}. This also corresponds to our observations. There 
        is one class (Rhabditophora) that contains all but one single exception of free-living species 
        of this phylum, which includes the Turbellaria. \\
      It should be noted, however, that this classification is outdated, as it has been proven that 
        the Turbellaria are not monophyletic. But we will not go into detail here. \\
      For the Platyhelminthes we have more state information for the leaf nodes compared to the other 
        considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
        0.1\% free-livings and predicted 0.77\% as free-living species. \\

      With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
        found only 5.32\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosen parasites 
        \cite{Blaxter1998}. In a recent article Blaxter identifies 18 origins \cite{Blaxter2015} in 
        Nematoda. \\
      The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species 
        are described by the Nematoda but it is assumed that one million or more species are in this 
        phylum.\footnote{J. Hallan, unpublished; 
          \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
          {https://insects.tamu.edu/research/collection/hallan/}
        }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
        with only 0.63\% (table \ref{table:results of some selected taxa}) free-living species. Against such 
        a shifted data situation, the algorithm is almost powerless to make correct predictions. And yet 
        the percentage has increased to 5.34\%. \\

      Origins: \\
      We go back to the same phyla as in the previous section: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      Chordata are full of free-living species and so we see only a few origins of parasitism. The root
      and mostly all species are predicted as free-living. \\
      In Apicomplexa and the Platyhelminthes also look credible. Our algorithm gives us only one loss of
        parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over
        mostly all species predicted as parasites. \\
      Nematoda is again \colorbox{red}{full of problems}. The root node is predicted as a parasite and so we have more 
        losses of parasitism for the less information of free-living species in this phylum. The rest 
        is parasitic \\
      As we have already mentioned Blaxter et al. found at least seven origins of parasitism 
        \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
        losses would have to turn around and become Origins. So it could be that we end up with a similar 
        size as Blaxter.

@@

    From the simulation, we can conclude that we predict correctly about 60\% of the nodes in the 
      present data situation (see section \ref{sec:results - simulation}).
    The leave-100-out cross-validation even showed that we predict the omitted nodes to be 98.17\%  
      percent correct (see section \ref{sec:results - cross-validation}). \\
    This allows for the assumption that the data is grouped and not uniformly distributed and thus 
      smaller subtrees are present in which data are to be found in the simulation with smaller 
      multifurcation and smaller value for unknown nodes. This is also confirmed by our biological 
      analysis of the Chordata subtree (see subsection \ref{subsec:results - statistics on predicted states}). \\
    However, this means that the ancestral states' data in the direction of root node are probably 
      particularly unbelievable. Which makes the localization of Origins direction root node 
      difficult. The question remains, how much this affects the estimation of the number of origins. 
      Our comparison with the paper from Weinstein and Kuris \cite{Weinstein2016} (see subsection 
      \ref{subsec:results - statistics on predicted states}), however, leaves us with optimism.

@@
